A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
Move things around, because I can

\paragraph{Top-Down Strategy} I'VE RE-ADDED A SHORTER VERSION OF THIS
PARAGRAPH, WHICH WAS COMMENTED OUT BY PATRICK. IT NEEDS WORK, BUT WE NEED TO
EXPLAIN THE SIP EXPERIMENT. We can modify the \McSplit\ algorithm to use a
top-down strategy based on \citet{UpcomingAAAIPaper} by calling the main
\FuncSty{McSplit} method once per goal size ($g, g-1, g-2, \dots$).  We
backtrack (\lineref{PruneSearch} of \cref{McCliqueAlg}) when the bound is
strictly less than the goal size, and terminate when a solution of the goal
size is found.

@@

\section{Comparison with Existing Algorithms}\label{sec:comparison} The
\McSplit\ algorithm may be considered as a version of the constraint
programming, forward-checking (CP-FC) algorithm of
\citet{DBLP:conf/cp/NdiayeS11}, using an efficient, compressed representation
of domains.  In the CP-FC algorithm, each vertex in $v \in \V(G)$ is
represented by a variable, whose domain corresponds to the set of vertices in
$\V(H)$ to which $v$ may currently be mapped, with an additional special $\bot$
value representing an unmapped vertex.

>>>>

@@

?? Let's put this hereish: I'VE RE-ADDED A SHORTER VERSION OF THIS
PARAGRAPH, WHICH WAS COMMENTED OUT BY PATRICK. IT NEEDS WORK, BUT WE NEED TO
EXPLAIN THE SIP EXPERIMENT. We can modify the \McSplit\ algorithm to use a
top-down strategy based on \citet{UpcomingAAAIPaper} by calling the main
\FuncSty{McSplit} method once per goal size ($g, g-1, g-2, \dots$).  We
backtrack (\lineref{PruneSearch} of \cref{McCliqueAlg}) when the bound is
strictly less than the goal size, and terminate when a solution of the goal
size is found.

\section{Comparison with Existing Algorithms}\label{sec:comparison}

The
\McSplit\ algorithm may be considered as a version of the constraint
programming, forward-checking (CP-FC) algorithm of
\citet{DBLP:conf/cp/NdiayeS11}, using an efficient, compressed representation
of domains.  In the CP-FC algorithm, each vertex in $v \in \V(G)$ is
represented by a variable, whose domain corresponds to the set of vertices in
$\V(H)$ to which $v$ may currently be mapped, with an additional special $\bot$
value representing an unmapped vertex.
